|

### 2024-12-05 output/seminar-slideshow.qmd
Extend probability curves through whole axis range
Previously, their domain seemed to be delimited to an interval constrained between the range of the axis breaks

PROB_AXIS      <- seq(-3, 3, by = .01)
ERROR_POINTS   <- seq(-3, 3, length.out = 5)
ITEM_LOADING   <-  0.45
ITEM_INTERCEPT <- -0.3

@@

# Plot: Upper Panel - Linear regression with Gaussian error distributions
latent_response |>
  ggplot(
    aes(x = response, y = point, fill = after_stat(x) > 0, group = point)
  )                            +
  geom_density_ridges_gradient(
    scale          =  .2,
    rel_min_height = 0.001,
    color          = PALETTE_BLUE["normal"]
  )                              +
  labs(x = "y~i~^*^", y = NULL)  +
  scale_y_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    labels       = NULL,
    limits       = range(ERROR_POINTS) * 1.12,
    expand       = expansion()
  )           +
  scale_x_continuous(breaks = 0) +
  scale_fill_manual(
    values = c(
      `FALSE` = unname(PALETTE_BLUE["white"]),
      `TRUE`  = unname(PALETTE_BLUE["normal"])
    )
  )                              +
  theme(
    axis.ticks.x = element_blank(),
    axis.title.y = element_markdown(angle = 90),
    legend.position = "none",
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH)
  )                              +
  coord_flip()
```
:::

@@

# Plot: Lower Panel - Probit curve
probit_curve_data |>
  ggplot(mapping = aes(x = score, y = prob))                        +
  geom_line(color = PALETTE_BLUE["normal"], linewidth = LINE_WIDTH) +
  labs(x = "E(*y~i~^*^*)", y = "P(Y~i~ = 1)")                       +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05)),
    oob = oob_keep
  )  +
  scale_x_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    limits = range(ERROR_POINTS) * 1.12,
    expand = expansion()
  ) +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
  )
```
:::
:::::
:::::::::

@@

logit_curve_data_long |>
  ggplot(
    mapping = aes(
      latent_trait, prob,
      color = item,
      group = after_scale(color)
    )
  )                                        +
  geom_line(linewidth = LINE_WIDTH)        +
  labs(x = "*&theta;*", y = "P(Y~i~ = 1)") +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05))
  )                                        +
  scale_x_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    limits = range(ERROR_POINTS) * 1.12,
    expand = expansion()
  )                                        +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
  )
```

>>>>

PROB_AXIS      <- seq(-3.3, 3.3, by = .01)
ERROR_POINTS   <- seq(-3, 3, length.out = 5)
ITEM_LOADING   <-  0.45
ITEM_INTERCEPT <- -0.3

@@

# Plot: Upper Panel - Linear regression with Gaussian error distributions
latent_response |>
  ggplot(
    aes(x = response, y = point, fill = after_stat(x) > 0, group = point)
  )                            +
  geom_density_ridges_gradient(
    scale          =  .2,
    rel_min_height = 0.001,
    color          = PALETTE_BLUE["normal"]
  )                              +
  labs(x = "y~i~^*^", y = NULL)  +
  scale_y_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    labels       = NULL,
    limits       = range(PROB_AXIS),
    expand       = expansion()
  )           +
  scale_x_continuous(breaks = 0) +
  scale_fill_manual(
    values = c(
      `FALSE` = unname(PALETTE_BLUE["white"]),
      `TRUE`  = unname(PALETTE_BLUE["normal"])
    )
  )                              +
  theme(
    axis.ticks.x = element_blank(),
    axis.title.y = element_markdown(angle = 90),
    legend.position = "none",
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH)
  )                              +
  coord_flip()
```
:::

@@

# Plot: Lower Panel - Probit curve
probit_curve_data |>
  ggplot(mapping = aes(x = score, y = prob))                        +
  geom_line(color = PALETTE_BLUE["normal"], linewidth = LINE_WIDTH) +
  labs(x = "E(*y~i~^*^*)", y = "P(Y~i~ = 1)")                       +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05)),
    oob = oob_keep
  )  +
  scale_x_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    limits = range(PROB_AXIS),
    expand = expansion()
  ) +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
  )
```
:::
:::::
:::::::::

@@

logit_curve_data_long |>
  ggplot(
    mapping = aes(
      latent_trait, prob,
      color = item,
      group = after_scale(color)
    )
  )                                        +
  geom_line(linewidth = LINE_WIDTH)        +
  labs(x = "*&theta;*", y = "P(Y~i~ = 1)") +
  scale_y_continuous(
    breaks       = 0:1,
    minor_breaks = NULL,
    limits       = 0:1,
    expand       = expansion(mult = c(0, .05))
  )                                        +
  scale_x_continuous(
    breaks       = ERROR_POINTS,
    minor_breaks = NULL,
    limits = range(PROB_AXIS),
    expand = expansion()
  )                                        +
  scale_color_manual(values = ITEMS_PALETTE, guide = NULL) +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17", linewidth = GRID_WIDTH),
  )
```
